### 2019-12-04 paper/paper.tex
Updates from Overleaf

\begin{lstlisting}[language = Julia]
# perform a merge sort on `v` using parallel threads
function psort(v::AbstractVector)
    hi = length(v)
    if hi < 100_000 # below some cutoff, run in serial
        return sort(view(v, 1:hi), alg = MergeSort)
    end
# split the range and sort the halves in parallel recursively
    mid = (1 + hi) >>> 1
    half = Threads.@spawn psort(view(v, 1:mid))
    right = psort(view(v, (mid + 1):hi))
    left = fetch(half)::typeof(right)
# perform the merge on the result
    out = similar(v)
    merge!(left, right, out)
    return out
end

function merge!(left, right, out)
    ll, lr = length(left), length(right)
    @assert ll + lr == length(out)
    i, il, ir = 1, 1, 1
    @inbounds while il <= ll && ir <= lr
        l, r = left[il], right[ir]
        if isless(r, l)
            out[i] = r
            ir += 1
        else
            out[i] = l
            il += 1
        end
        i += 1
    end
    @inbounds while il <= ll
        out[i] = left[il]
        il += 1
        i += 1
    end
    @inbounds while ir <= lr
        out[i] = right[ir]
        ir += 1
        i += 1
    end
    return out
end
\end{lstlisting}

@@

\lstDeleteShortInline|
\begin{table}[ht]
\tbl{Measured timing of the examples given above.}{
\begin{tabular}{ |l l l l l| }
    \hline
    nthreads & 1 & 2 & 3 & 4 \\
    \hline
    S61\_SIEVE & 14.704s & 7.709s & 4.065s & 2.241s \\
    psort & 2.609s & 1.528s & 1.321s & 0.993s \\
    prefix\_threads! & 2.375s & 1.462s & 1.100s & 1.043s \\
    \hline
\end{tabular}}
\label{table:timings}
\end{table}

@@

\begin{lstlisting}[language = Julia, inputencoding = utf8, literate = {÷}{{$\div$}}1]
function pmerge!(left, right, out)
    ll, lr = length(left), length(right)
    @assert ll + lr == length(out)
    if length(out) < 100_000
        # below some threshold, just do the merge
        merge!(left, right, out)
    else
        # split the larger chunk in half, then binary search the
        # smaller half to split it
        if ll > lr
            jl = ll ÷ 2
            # stable sort: find the last entry in right
            # strictly smaller than l
            jr = searchsortedfirst(right, left[jl]) - 1
        else
            jr = lr ÷ 2
            # stable sort: find the last entry in left not bigger
            # than r
            jl = searchsortedlast(left, right[jr])
        end
        @sync begin
            let left = view(left, 1:jl),
                right = view(right, 1:jr),
                out = view(out, 1:(jl + jr))
                Threads.@spawn pmerge!(left, right, out)
            end
            let left = view(left, (jl + 1):ll),
                right = view(right, (jr + 1):lr),
                out = view(out, (jl + jr + 1):length(out))
                pmerge!(left, right, out)
           end
        end
    end
    nothing
end
\end{lstlisting}

>>>>

\begin{lstlisting}[language = Julia]
# perform a merge sort on `v` using parallel threads
function psort(v::AbstractVector)
    hi = length(v)
    if hi < 100_000 # below some cutoff, run in serial
        return sort(v, alg = MergeSort)
    end
# split the range and sort the halves in parallel recursively
    mid = (1 + hi) >>> 1
    half = Threads.@spawn psort(view(v, 1:mid))
    right = psort(view(v, (mid + 1):hi))
    left = fetch(half)::typeof(right)
# perform the merge on the result
    out = similar(v)
    merge!(out, left, right)
    return out
end

function merge!(out, left, right)
    ll, lr = length(left), length(right)
    @assert ll + lr == length(out)
    i, il, ir = 1, 1, 1
    @inbounds while il <= ll && ir <= lr
        l, r = left[il], right[ir]
        if isless(r, l)
            out[i] = r
            ir += 1
        else
            out[i] = l
            il += 1
        end
        i += 1
    end
    @inbounds while il <= ll
        out[i] = left[il]
        il += 1
        i += 1
    end
    @inbounds while ir <= lr
        out[i] = right[ir]
        ir += 1
        i += 1
    end
    return out
end
\end{lstlisting}

@@

\lstDeleteShortInline|
\begin{table}[ht]
\tbl{Measured timing of the examples given above.}{
\begin{tabular}{ |l l l l l| }
    \hline
    nthreads & 1 & 2 & 3 & 4 \\
    \hline
    S61\_SIEVE & 14.704s & 7.709s & 4.065s & 2.241s \\
    psort & 2.609s & 1.528s & 1.321s & 0.993s \\
    prefix\_threads! & 2.375ms & 1.462ms & 1.100ms & 1.043ms \\
    \hline
\end{tabular}}
\label{table:timings}
\end{table}

@@

\begin{lstlisting}[language = Julia, inputencoding = utf8, literate = {÷}{{$\div$}}1]
function pmerge!(out, left, right)
    ll, lr = length(left), length(right)
    @assert ll + lr == length(out)
    if length(out) < 100_000
        # below some threshold, just do the merge
        merge!(out, left, right)
    else
        # split the larger chunk in half, then binary search the
        # smaller half to split it
        if ll > lr
            jl = ll ÷ 2
            # stable sort: find the last entry in right
            # strictly smaller than l
            jr = searchsortedfirst(right, left[jl]) - 1
        else
            jr = lr ÷ 2
            # stable sort: find the last entry in left not bigger
            # than r
            jl = searchsortedlast(left, right[jr])
        end
        @sync begin
            let left = view(left, 1:jl),
                right = view(right, 1:jr),
                out = view(out, 1:(jl + jr))
                Threads.@spawn pmerge!(out, left, right)
            end
            let left = view(left, (jl + 1):ll),
                right = view(right, (jr + 1):lr),
                out = view(out, (jl + jr + 1):length(out))
                pmerge!(out, left, right)
           end
        end
    end
    nothing
end
\end{lstlisting}
